---
title: "Gapminder"
author: "Dean Stewart"
date: "08/03/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#tinytex::install_tinytex()
library(tidyverse)
library(gapminder)
```

## Introduction

In this document, we will be exploring the Gapminder dataset.

## Observations of Gapminder

### Countries with life expectancy greater than 81

```{r life over 80, echo=TRUE}
gapminder1 <- gapminder %>% filter(lifeExp > 81)
gapminder1
```

There are `r length(gapminder1) + 1` countries with life expectancy *over* **81**!

### Life Expectancy by continent in 2007

```{r}
gapminder2 <- gapminder %>% filter(year == 2007) 
boxplot(lifeExp~continent,data=gapminder2)
```

* In 2007, Oceania had the highest median life expectancy, followed by Europe, Americas, Asia and lastly Africa.  

```{r, include=FALSE}
country <- gapminder2$country[which.max(gapminder2$lifeExp)]
```

* One of the countries in Asia however had the highest life expectancy in 2007. This was `r country` . 

